---
title: "Load Default Simulator"
author: "Yuvaraj"
date: "15/09/2020"
output: html_document
---
This program does the following

- Assume **8%-10%** of defaults
- Categorize them to *3 buckets*
- Does not do any Data ~~Analysis~~
- Draw graph for a month
- [Visit to learn R Markdown] (https://rmarkdown.rstudio.com/)

## Load Defaults

This is a sample program to create a load default **simulation**
This sample create *100* sample accounts for *36* months and sets defaulter list based on the **%** of input in **3 buckets**

```{r, echo=FALSE}
#Define Constants
loan_tenure <- 36
no_of_accounts <-100
bk1_default_per=8
bk2_default_per=12
bk3_default_per=8
bk4_default_per=4
str_month <- "MN"
str_account<-"AC"
xdm<-NULL
#create Months list
nm<-NULL
nm<-1:loan_tenure
#Create Account Name
account_names<-NULL
account_names<-paste(str_account, seq(1:no_of_accounts), sep="")
month_names<-NULL
month_names<-paste(str_month, seq(1:loan_tenure), sep="")
xdm<-NULL
xdm<-matrix(nrow = no_of_accounts, ncol=loan_tenure, dimnames = list(account_names, month_names))
# define buckets range samples of paymentDoneTrue
bx<-loan_tenure/3
bucket1<-seq(1,bx)
bucket2<-seq(bx+1,2*bx)
bucket3<-seq(2*bx+1,3*bx)
bucket4<-seq(3*bx+1,4*bx)
# Simulate defaulters
b1<-NULL
b1<-sample (c(1,0), no_of_accounts, replace=T, prob=c((1-bk1_default_per/100),bk1_default_per/100))

xdm[,1:bx]<-b1
#Set 8% of defaults in bucket 1
b2<-NULL
b2<-sample (c(1,0), no_of_accounts, replace=T, prob=c((1-bk2_default_per/100),bk2_default_per/100))
xdm[,(bx+1):(2*bx)]<-b2
b3<-NULL
b3<-sample (c(1,0), no_of_accounts, replace=T, prob=c((1-bk3_default_per/100),bk3_default_per/100))
xdm[,(2*bx+1):(3*bx)]<-b3
```
## Summary for Month1
```{r echo=FALSE}
summary(xdm[,"MN1"])
```

### Graph for Month 1
```{r xdm, echo=FALSE}
plot(xdm[,"MN1"], type = "o" )
```
